Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
another pass on discussion

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each of the engines we were able to
find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
successful technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), and (iii) to cover a case of
rejected bug report.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
code snippet below shows an example input related to a bug report that
we issued to the \chakra\ development team, but they did not accept.
This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. Instead of the long integer passed as
argument to \CodeIn{"foo".repeat()}, the original test used the
integer literal 3. The engine crashes on this input as result. The
team answered that this was an incompatibility by design as the
function repeat was not expected to receive such a long value.

@@

\subsection{Threats}

>>>>

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each of the engines we were able to
find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
successful technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
rejected bug report, and (iv) the test is short.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
code snippet below shows an example input related to a bug report that
we issued to the \chakra\ development team, but they did not accept.

@@

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. Instead of the long integer passed as
argument to \CodeIn{"foo".repeat()}, the original test used the
integer literal 3. The engine crashes on this input as result. The
team answered that this was an incompatibility by design as the
function repeat was not expected to receive such a long value.

\subsection{Threats To Validity}
